---
title: "DimensionReduction_Clustering"
author: "Yasin Kaymaz"
date: "04/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library(DT)
options(width = 80)
source("https://raw.githubusercontent.com/yasinkaymaz/cellRtools/master/main/functions.R")
```

```{r echo=FALSE}
load("~/data/TCGA/LungCancerGDC.sub.seurat.Robj")
```

## Clustering analysis of all samples in the study

In each of these plots, colored dots represent individual sample. Analysis was done using only highly variable genes. Sample annotation are projected from the data repository.



### **PCA plots**

Principal components analysis of RNAseq data of tumor/normal tissues from patients diagnoses either with Adenocarcinoma or Squamous cell carcinoma.

```{r echo=FALSE, fig.height=8, fig.width=10}

PCAPlot(Lc.sub, group.by="name", pt.size=2)
PCAPlot(Lc.sub, group.by="definition", pt.size=2)
```


### **UMAP plots**

Uniform Manifold Approximation and Projection (UMAP) plots of samples based on highly variable genes. Each dot represents a sample colored by various sample/patient clinicial feature. 

```{r echo=FALSE, fig.height=8, fig.width=10}
DimPlot(object = Lc.sub, reduction = "umap", group.by="gender", pt.size=2)
DimPlot(object = Lc.sub, reduction = "umap", group.by="name", pt.size=2)
DimPlot(object = Lc.sub, reduction = "umap", group.by="definition", pt.size=2)
DimPlot(object = Lc.sub, reduction = "umap", group.by="ClassType", pt.size=2)#--> The most informative
DimPlot(object = Lc.sub, reduction = "umap", group.by="race", pt.size=2)
DimPlot(object = Lc.sub, reduction = "umap", group.by="ethnicity", pt.size=2)
DimPlot(object = Lc.sub, reduction = "umap", group.by="primary_diagnosis", pt.size=2)
DimPlot(object = Lc.sub, reduction = "umap", group.by="tumor_stage", pt.size=2)
DimPlot(object = Lc.sub, reduction = "umap", group.by="vital_status", pt.size=2)
DimPlot(object = Lc.sub, reduction = "umap", group.by="tissue_or_organ_of_origin", pt.size=2)
```



.

.

.

.

.
